Pulled Pork: 

**Bake for 6 to 8 hours

2 tsp salt 
1 tsp black pepper
1 TBSP liquid smoke
2 tsp oil 
1 medium Onion choppped
4 cloves garlic minced
2 tsp tomato paste 
1 TBSP chili powder
2 tsp ground cumin
1 Cup of water
3 TBSP apple cider vinegar
1 TBSP worcester sauce

Jubilee Jumbles 

*** bake 10 - 13 minutes at 375 degrees.  
1/2 cup soft shortening 
1 cup brown sugar 
1/2 cup white sugar
2 eggs
1 cup sour cream (or evaporated milk)
a tsp vanilla extract
2 3/4 cup flour 
1/2 tsp baking soda
1 tsp salt 
1 cup black walnuts 

Helens Stuffed bell peppers 

*** Cook in stove or in slow cooker
2 lbs ground beef 
3 eggs 
1 chopped onion 
2 cups of rice 
a pinch of salt and pepper 
a spoonful of garlic 
 

Stuff into bell peppers and then throw them in oven 
Great with mash potatoes

Strawberry or Cherry Cream Cheese Cobbler

Use Cherries from freezer: If handpicked 
Gene Loved this dish


*** Preheat over 350 degrees melt butter in a 9x13 glass dish. 
Mix egg, flour, milk, sugar, baking powder, and salt pour directly over the baking dish do not stir
add strawberries or cherries in a single layer spread cream cheese pieces over stawberreis and cherries 
bake at 420 deggries for 45 minutes until golden brown and edges are bubbling crust rises up around the fruit.  
1 stick butter melted
1 egg beaten 
1 cup milk 
1/2 tsp salt 
1 cup flour 
1 cup sugar 
2 tsp baking powder
2 quarts strawberries 
4 oz cream cheese
4 or 5 cups of frozen sour cherries 


Strawberry Bannana Cheesecake Salad 

Combine cream cheese, pudding mix and coffee creamer do not pour creamer in cream cheese all at once makes it 
clumpy 
1 8 oz package cream cheese softened 
1 3.4 ounce Package instant cheesecake flavored pudding, unprepared
1 cup French vanilla creamer, liquid
2 lb strawberries
3 Bannanas
2 TBSP lemon juice
1 8 oz container of cool whip
use electric mixer to beat cream cheese until smooth add dry pudding mix and beat until smooth slowly add creamer to cream cheese mixture and beat until smooth.  
Let chill for 1 hour.  Wash and slice strawberries and bananas.  Toss with lemon juice.  When ready to serve fold in cool whip.  Serve immediately.

